\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-09-03 jss/article.tex
edit by Tak on 3 Sep

\subsection{Pseudo-data Generation Process}
Figure \ref{fig:pseudo} will be helpful to understand this process. As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$. So, once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given. Then using (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}, $ where $i$ indicates the $i$-th simulation.

@@

So, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
\begin{equation}
\widehat{Var}(\bar{I}_{j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I^{(i)}_{j}-\bar{I}_{j})^{2},~ j=1, 2, \ldots, k.
\end{equation}

\subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into consideration. Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset. 
\begin{equation}\label{RB}
\bar{I}_{RB, j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta),~ j=1, 2, \ldots, k.
\end{equation}

@@

Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 15 times smaller than that of simple one. It means that 1,000 RB unbiased coverage estimates are as precise as 15,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.

@@

It is evident in the shrinkage and 95\% interval plots in Figure \ref{fig:baseball} that shrinkage occurs from the sample means (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310. For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other. For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.

@@

As in the previous examples in Sections \ref{sec:ex:hosp} and \ref{sec:ex:8schools} to check the level of trust in these interval estimates a method check can be undertaken by assuming the estimates, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, are true values. For reference, to do the method check at different true values additional arguments can be specified in the coverage function.

@@

@@

A benefit of \pkg{Rgbp} is that it produces non-random output, unlike most MCMC methods,  and so results can easily be reproduced and compared across studies. In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure. Such as being used to

\begin{enumerate}
\item to initialize an MCMC to speed up time to convergence.
\item to check the validity of the code of an MCMC program.
\item as evaluated modules in object-oriented programming.
\item for preliminary data analyses.
\item as a demo that a particular prior gives adequate coverage.
\item for frequentist procedure checking (via bootstrapping).
\item for model checking.
\item to see if there is any reason to develop and use a more precise shrinkage method.

>>>>

\subsection{Pseudo-data Generation Process}
Figure \ref{fig:pseudo} will be helpful to understand this process. As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$. So, once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given and the superscript $(i)$ indicates the $i$-th simulation. Then using (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.

@@

Then, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
\begin{equation}
\widehat{Var}(\bar{I}_{j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I^{(i)}_{j}-\bar{I}_{j})^{2},~ j=1, 2, \ldots, k.
\end{equation}

\subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into account. Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset. 
\begin{equation}\label{RB}
\bar{I}_{RB, j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta),~ j=1, 2, \ldots, k.
\end{equation}

@@

Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 15 times smaller than that of simple one. It means that 1,000 RB unbiased coverage estimates are as precise as 15,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.

@@

It is evident in the shrinkage plot in Figure \ref{fig:baseball} that shrinkage occurs from the sample means (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310. For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other. For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.

@@

As in the previous examples in Sections \ref{sec:ex:hosp} and \ref{sec:ex:8schools} to check the level of trust in these interval estimates a method check can be undertaken by assuming the estimates, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, are true values.

@@

For reference, to do the method check at different true values additional arguments can be specified in the coverage function. For example, if we want to try different true values, either 100 for $r$ or (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the additional arguments are \code{A.or.r = 100} and \code{reg.coef = c(-1, 0.2)}; \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of the above code.

@@

A benefit of \pkg{Rgbp} is that it produces non-random output, unlike most MCMC methods,  and so results can easily be reproduced and compared across studies. In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure. Such as being used

\begin{enumerate}
\item to initialize an MCMC to speed up time to convergence.
\item to check the validity of the code of an MCMC program.
\item as evaluated modules in object-oriented programming.
\item for preliminary data analyses.
\item as a demo that a particular prior gives adequate coverage.
\item for frequentist procedure checking.
\item for model checking.
\item to see if there is any reason to develop and use a more precise shrinkage method.
